### 2023-02-02 definitions.tex
details

\problemx{uniform resilience problem}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $SAFE, BAD \subseteq S$.}
{$BAD \longrightarrow^{*} SAFE$ ?\newline}
%
%\alain{il faudrait ne pas répéter 3 fois les mêmes imputs pour les 3 pbs: énoncer les 3 uniformes pbs d'un coup avec une fois l'input puis les 3 pbs pour un état s donné sans répéter non plus 3 fois les mêmes inputs}

\problemx{uniform $k$-resilience problem}
{A transition system $\mathscr{S}=(S,\rightarrow), k \in \mathbb{N}$ and two sets $SAFE, BAD \subseteq S$.}
{$BAD \longrightarrow^{\leq k} SAFE$ ?\newline}

We add a third problem that decides whether there exists an $k$ such  that the system is $k$-resilient.
%
\problemx{uniform bounded resilience problem}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $SAFE, BAD \subseteq S$.}
%{$\exists k \geq 0 ~ \forall s' \in D ~ s \rightarrow^* s' \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}
{$\exists k \geq 0$ such that $\mathscr{S}$ is $k$-resilient ?\newline}

@@

For instance, the well-known mutual exclusion property is often modelized in a $d$-counters machine by the property that a counter $c_{mutex}$ must be bounded by (usually) one. Then, the set $SAFE =  \{c_{mutex} \leq 1\} \times \mathbb{N}^{d-1}$ is downward closed and $BAD =\{c_{mutex} \geq 2\} \times  \mathbb{N}^{d-1} $ is the upward closed complementary of SAFE. In \cite{DBLP:conf/gg/Ozkan22}, the authors considered that BAD is always downward closed and SAFE is always upward closed.
%

@@

>>>>

\problemx{uniform resilience problem (URP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $SAFE, BAD \subseteq S$.}
{$BAD \longrightarrow^{*} SAFE$ ?\newline}
%
%\alain{il faudrait ne pas répéter 3 fois les mêmes imputs pour les 3 pbs: énoncer les 3 uniformes pbs d'un coup avec une fois l'input puis les 3 pbs pour un état s donné sans répéter non plus 3 fois les mêmes inputs}

\problemx{uniform $k$-resilience problem (UkRP)}
{A transition system $\mathscr{S}=(S,\rightarrow), k \in \mathbb{N}$ and two sets $SAFE, BAD \subseteq S$.}
{$BAD \longrightarrow^{\leq k} SAFE$ ?\newline}

We add a third problem that decides whether there exists an $k$ such  that the system is $k$-resilient.
%
\problemx{uniform bounded resilience problem (UBRP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $SAFE, BAD \subseteq S$.}
%{$\exists k \geq 0 ~ \forall s' \in D ~ s \rightarrow^* s' \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}
{$\exists k \geq 0$ such that $\mathscr{S}$ is $k$-resilient ?\newline}

@@

For instance, the well-known mutual exclusion property is often modelized in a $d$-counters machine by the property that a counter $c_{mutex}$ must be bounded by (usually) one. Then, the set $SAFE =  \{c_{mutex} \leq 1\} \times \mathbb{N}^{d-1}$ is downward closed and $BAD =\{c_{mutex} \geq 2\} \times  \mathbb{N}^{d-1} $ is the upward closed complementary of SAFE. In \cite{DBLP:conf/gg/Ozkan22}, the authors considered that BAD is always downward closed and SAFE is always upward closed.
%		
In what follows, we will always suppose that a downward closed set $D$ is given by its finite set of ideals $I(D)$ satisfying $D=\downarrow D =I(D) \cap S$and that an upward closed set $U$ is given by its finite set of minimal elements, $b(U)$.

@@

\begin{proposition}\label{down-up}
Let $\mathscr{S}$ be an effective WSTS with effective predbasis and let the two finite sets $I(BAD)$ and  $b(SAFE)$ representing $\downarrow BAD$ and $\uparrow SAFE$.
The uniform resilience problem (URP), the uniform bounded resilience problem (UBRP) and the uniform $k$-resilience problem (UkRP) are decidable
\end{proposition}

\begin{proof}
The uniform resilience problem (URP) reduces to decide coverability of the finite set $b(SAFE)$ from the infinite set $BAD$; but it is sufficient to decide coverability from the finite set of maximal elements of $BAD$ which are ideals but not elements in $S$. We use the fact that y is coverable from an $x \in BAD$ iff $y$ is coverable from $x' \in I(BAD)$.

Hence it is decidable since
uniform bounded resilience problem (UBRP) is equivalent to the uniform resilience problem (UBRP) for WSTS with...
The uniform $k$-resilience problem (UkRP) is also decidable by computing the least $n$ such that $\pred^n(SAFE)=\pred^*(SAFE)$ and then to test whether $n \leq k$.
\end{proof}
